Behavior Driven Development in Haskell

### 2012-05-23 paper.tex
fixing mistakes.

\begin{quote}
\begin{verbatim}
> length []
0
\end{verbatim}
\end{quote}

@@

\begin{quote}
\begin{verbatim}
> writeFile "tmpfile" "Hello"
> readFile "tmpfile"
"Hello"
\end{verbatim}
\end{quote}

@@

Haddock also provides code block annotations indicated wwith ({\tt >}).
For example, the {\tt container} packages has the following code block annotation:

\begin{quote}
\begin{verbatim}
>>> Data.Map.null (empty) == True
\end{verbatim}
\end{quote}

@@

\begin{quote}
\begin{verbatim}
> Data.Map.null (empty)
True
\end{verbatim}
\end{quote}

>>>>

\begin{quote}
\begin{verbatim}
>>> length []
0
\end{verbatim}
\end{quote}

@@

\begin{quote}
\begin{verbatim}
>>> writeFile "tmpfile" "Hello"
>>> readFile "tmpfile"
"Hello"
\end{verbatim}
\end{quote}

@@

Haddock also provides code block annotations indicated with ({\tt >}).
For example, the {\tt container} packages has the following code block annotation:

\begin{quote}
\begin{verbatim}
> Data.Map.null (empty) == True
\end{verbatim}
\end{quote}

@@

\begin{quote}
\begin{verbatim}
>>> Data.Map.null (empty)
True
\end{verbatim}
\end{quote}
